Social Feedback For Robotic Collaboration

### 2016-05-22 paper.tex
fixed related work

We will solve this problem by formulating it as a Partially Observable Markov Decision Process (POMDP)\citep{kaelbling99}, which will allow us to dynamically and flexibly determine how to choose social feedback actions. First, we will describe a two agent model and use this to motivate the construction of a POMDP. The crucial improvement we make over existing robot interaction models is that we maintain a state variable that tracks the human's interpretations of the actions the robot takes. We will next discuss how we solved this POMDP and other measures we took to allow our system to respond dynamically and fluidly.

@@

This work is primarily built off of \cite{eldon15thesis}, which describes a system for incremental speech and gesture recognition in an object-delivery domain. In previous work \citep{socialfeedback}, the model from \cite{eldon15thesis} is expanded from a bayesian inference model into a POMDP model that can ask yes-no questions. In this work, we generalize the idea of the affect of robot's actions on humans state within a POMDP framework.

@@

Other work with collaborative robots exists, for example, \cite{foster12} have done research with a bar-tending robot. This robot follows a rule-based state estimator, and delivers drinks from fixed positions behind the bar to multiple users based on their speech and torso position. 
We expand the scope of the problem: we do not use a rule-based state planner, our items are not in fixed positions, and our gesture model uses pointing instead of torso position.

In \cite{bohus14},  a robotic building guide directs guests to find specific rooms. Our project addresses a similar domain, requiring the interpretation of users' requests, but differs in the task and the type of communication necessary to accomplish that task.

Other work involving robotic object delivery also exists. Some approaches have no social feedback and will either deliver the wrong item or do nothing if given a
request it does not understand~\citep{tellex11,matuszek12,tellex12,misra14}. Language only feedback models also 
exist~\citep{chai14,macmahon06,tellex11,matuszek12,guadarrama14,hewlett11,misra14}, and several gesture only models~\citep{waldherr00,marge11}.

\cite{matuszek14} shows promising work in fusing language and complex gesture to understand references to multiple objects at once. We build off this work by including social feedback.

In the field of computational linguistics, previous work exists in resolving referring expressions incrementally, such as~\cite{schlangen09,Zender2008Conceptual,Gieselmann}. Other work in that community also incorporates gesture, and/or eye gaze~\citep{kennington13,kennington15a}, but the given work does not incrementally update gesture along with speech. ~\cite{chairmi} provides work towards resolving referring expressions in a different domain, but does not address the task of acting on the results of these referring expressions. In~\cite{kruijffclarification}, they propose a system for planning to ask for clarifications, which covers a wide scope of knowledge failures. In this work, we are interested only in a small subset of these clarifications, and address the problem of how and when these clarifications should be used in a concrete human-robot collaboration task.

@@

Markov Decision Processes (MDPs) are models that describe how an agent can take actions to transition between states, receiving rewards for its actions. Partially Observable Markov Decision Processes (POMDPs) are used to model MDPs where the true state is not known. Instead, the agent receives observations that are generated by the true state, and must infer what the true state is from the observations. Thus, the agent maintains a belief over true states which is updated as it receives new observations. In subsequent sections, we will refer to this belief over hidden states as $b$. The agent must then use this belief state to determine which action to take to maximize its expected value of the reward over time. This splits the POMDP into two main components, a state estimator and a policy generator. A typical graphical model for a POMDP is provided in figure~\ref{fig:pomdp}.\footnote{In this model, we have omitted the dependency between an action and the observation from the next timestep. In the POMDP discussed in this paper, we will not use this dependency for any action. Rather, the affect of the actions on the observation is encapsulated in the state.}

\tikzstyle{h} = [circle, draw, fill=white, minimum size=3em]
\tikzstyle{a} = [diamond, draw, fill=gray!40, minimum size=3em]
\tikzstyle{v} = [circle, draw, fill=gray!40, minimum size=3em]
\tikzstyle{line} = [draw, > = stealth, -latex]

@@

WE represent human states $s_t$, robot states $\sigma_\tau$, and observations generated by the robot $\omega_\tau$ and by the human $o_{t}$. Observe that the structure of this model resembles two POMDPs combined together at their actions and observations. The lower POMDP is the POMDP from the human's perspective: the robot has some hidden states $\sigma_\tau$, which the human observes by means of $\omega_{t}$. The human takes actions $o_{t}$ to influence the robot's state $\sigma_t$. The upper POMDP models the interaction from the robot's perspective: the human's state $s_t$ is hidden from the robot, and the robot must infer it from observations $o_{t}$. When the robot takes action $\omega_{\tau-1}$, it affects the human's state $s_t$. Crucially, each agent treats the other agent's action as an observation that influences their belief about the other agent's hidden state. Thus, the human's actions affect the robot's belief about the human's state, which is what we call $b$ above. Importantly, the reverse is also true: the robot's actions affect the human's belief about what the robot's hidden state is. We will call the human's belief over the robot's hidden state $\beta$.

@@

	\item The set of actions A consists of both social and non-social actions. Non-social actions are \texttt{pick(i)} (picking up  and delivering an object $i$) and \texttt{wait}. Social actions are \texttt{point(x)}, pointing at a location $x$; \texttt{look(x)}, looking at a location $x$;\footnote{$x$ is chosen from the set of points that describe the surface of the table. For computational reasons, in this work, we restrict it to the set of object locations} and \texttt{say(p)}, informing the human that the robot believes the desired object has property $p$, where $p$ is an element of some object's vocabulary. 

@@

\subsection{User Studies Procedure}

\exwnote{Will rewrite this if/when we run user studies}

Users are acquired from convenience sampling by inviting volunteers from the Brown University CIT building. For each user, two trials are run: a baseline trial without any social feedback actions, and a social-feedback trial with social feedback actions enabled. For each trial, the user is given a microphone and invited to use speech and gesture to ask the robot for a specific item on the table, and to not change that object until it was picked up. After their requested object is picked up, they request a new object and repeat the procedure until the robot has handed them all objects on the table. It is decided randomly whether the social or non-social trial is performed first for each user. Between the two trials, they are given a survey to assess the qualitative aspects of the interaction, including metrics such as the robot's perceived intelligence, friendliness, etc.

This procedure is based off a previous user study run for an earlier iteration of this project. In this user study, we noticed a small effect showing the increased speed of interaction with social feedback actions enabled. However, this study was run with only six participants, so these effects were likely not statistically significant. When user studies are run in the future, we will have a larger sample size, but also increase the difficulty of the task by adding more objects, which should further highlight the necessity of social feedback.

Interesting metrics to measure include are how the perception of the robot is correlated to the actions the robot takes, as well as the accuracy and speed of the interaction. We may also consider a longer-running user study to investigate how people learn how to interact with the robot.

>>>>

We will solve this problem by formulating it as a Partially Observable Markov Decision Process (POMDP)\citep{kaelbling99}, which will allow us to dynamically and flexibly determine how to choose social feedback actions. First, we will describe a two agent model and use this to motivate the construction of a POMDP. The crucial improvement we make over existing robot interaction models is that we maintain a state variable that tracks the human's interpretations of the actions the robot takes.

@@

This work is primarily built off of \citet{eldon15thesis}, which describes a system for incremental speech and gesture recognition in an object-delivery domain. In previous work\citep{socialfeedback}, the model from \citet{eldon15thesis} is expanded from a bayesian inference model into a POMDP model that can ask yes-no questions. In this work, we generalize the idea of the affect of robot's actions on humans state within a POMDP framework.

@@

Other work with collaborative robots exists, for example, \citet{foster12} which describes research done with a bar-tending robot and \citet{bohus14}, where a robotic building guide directs guest to specific rooms. We focus on collaboration within the domain of object delivery, with a focus on avoiding rule-based methods that balance information collection with exploration via a POMDP.

Many other works have addressed the object delivery domain. Some approaches have no social feedback and will either deliver the wrong item or do nothing if given a
request it does not understand~\citep{tellex11,matuszek12,tellex12,misra14}. Language only feedback models also 
exist~\citep{chai14,macmahon06,tellex11,matuszek12,guadarrama14,hewlett11,misra14}, and several gesture only models~\citep{waldherr00,marge11}. We supplement gesture and language interpretation with social feedback, allowing the robot to respond.

In the field of computational linguistics, previous work exists in resolving referring expressions incrementally, such as~\citet{schlangen09,Zender2008Conceptual,Gieselmann}. Other work in that community also incorporates gesture, and/or eye gaze~\citet{kennington13,kennington15a}, but the given work does not incrementally update gesture along with speech. ~\cite{chairmi} provides work towards resolving referring expressions in a different domain, but does not address the task of acting on the results of these referring expressions. In~\citet{kruijffclarification}, they propose a system for planning to ask for clarifications, which covers a wide scope of knowledge failures. In this work, we are interested only in a small subset of these clarifications, and address the problem of how and when these clarifications should be used in a concrete human-robot collaboration task.

@@

Markov Decision Processes (MDPs) are models that describe how an agent can take actions to transition between states, receiving rewards for its actions. Partially Observable Markov Decision Processes (POMDPs) are used to model MDPs where the true state is not known. Instead, the agent receives observations that are generated by the true state, and must infer what the true state is from the observations. Thus, the agent maintains a belief over true states which is updated as it receives new observations. In subsequent sections, we will refer to this belief over hidden states as $b$. The agent must then use this belief state to determine which action to take to maximize its expected value of the reward over time. This splits the POMDP into two main components, a state estimator and a policy generator. A typical graphical model for a POMDP is provided in figure~\ref{fig:pomdp}.
\tikzstyle{h} = [circle, draw, fill=white, minimum size=3em]
\tikzstyle{a} = [diamond, draw, fill=gray!40, minimum size=3em]
\tikzstyle{v} = [circle, draw, fill=gray!40, minimum size=3em]
\tikzstyle{line} = [draw, > = stealth, -latex]

@@

We represent human states $s_t$, robot states $\sigma_\tau$, and observations generated by the robot $\omega_\tau$ and by the human $o_{t}$. Observe that the structure of this model resembles two POMDPs combined together at their actions and observations. The lower POMDP is the POMDP from the human's perspective: the robot has some hidden states $\sigma_\tau$, which the human observes by means of $\omega_{t}$. The human takes actions $o_{t}$ to influence the robot's state $\sigma_t$. The upper POMDP models the interaction from the robot's perspective: the human's state $s_t$ is hidden from the robot, and the robot must infer it from observations $o_{t}$. When the robot takes action $\omega_{\tau-1}$, it affects the human's state $s_t$. Crucially, each agent treats the other agent's action as an observation that influences their belief about the other agent's hidden state. Thus, the human's actions affect the robot's belief about the human's state, which is what we call $b$ above. Importantly, the reverse is also true: the robot's actions affect the human's belief about what the robot's hidden state is. We will call the human's belief over the robot's hidden state $\beta$.

@@

	\item The set of actions $A$ consists of both social and non-social actions. Non-social actions are \texttt{pick(i)} (picking up  and delivering an object $i$) and \texttt{wait}. Social actions are \texttt{point(x)}, pointing at a location $x$; \texttt{look(x)}, looking at a location $x$;\footnote{$x$ is chosen from the set of points that describe the surface of the table. For computational reasons, in this work, we restrict it to the set of object locations} and \texttt{say(p)}, informing the human that the robot believes the desired object has property $p$, where $p$ is an element of some object's vocabulary. 

@@
